---
title: "Orientation Computing Lab"
author: "Jaihee Choi"
date: '2022-08-15'
output: pdf_document
---

This is a very simple tutorial for using RMarkdown

\section*{How to output a plot}
```{r ex1, echo=TRUE}
# define x and y
x <- 1:10
y <- x^2

#plot the points
plot(x,y)
```

The plot above shows $y = x^2$.

\newpage
\section*{Utilizing the chunk options to display what you want}
```{r ex2, echo= TRUE}
a <- -1:10
b <- log(a)

print(b)
```

We want the above output without the warning
```{r ex3, echo = TRUE, warning = FALSE}
a <- -1:10
b <- log(a)

#print the results
print(b)
```

\subsection*{Using real data}

```{r ex4, echo = T, message = F, warning = F}
# Fit the linear regression using the mtcars dataset
fit <- lm(mpg ~ wt, data = mtcars)

# print the coefficients
fit$coefficients

```

Now print without the code showing:

```{r ex5, echo = F, message = F, warning = F}
# Fit the linear regression using the mtcars dataset
fit <- lm(mpg ~ wt, data = mtcars)

# print the coefficients
fit$coefficients

```



\newpage

\section*{Rmd syntax}

The main text is the same as linux commands.\\
For example, if I wanted to type an equation, I would use 
\begin{verbatim}
$$y = x^2$$
\end{verbatim}

which would look like 
$$y = x^2$$
If I wanted an equation intext, like $a^2 + b^2 = c^2$, I would just use '\$\$'. For example:
\begin{verbatim}
The Pythagorean Theorem is $a^2 + b^2 = c^2$.
\end{verbatim}


Latex is also very helpful for the ease of using symbols.
For example, typing:
\begin{verbatim}
$\alpha, \beta, \delta, \Omega, \pi$
\end{verbatim}

Gives you $\alpha, \beta, \delta, \Omega, \pi$


